---
title: "week 1, ignore me"
author: "Marie Han"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(boot))
suppressPackageStartupMessages(library(stringr))
```

```{r}

input_2023_w01 <- read.csv("C:/Users/marie/Downloads/nfl-big-data-bowl-2026-prediction/train/input_2023_w01.csv")
avg_speed_by_player <- function(data) {
  data %>%
    group_by(player_name) %>%
    summarize(avg_speed = mean(s, na.rm = TRUE)) %>%
    arrange(desc(avg_speed))
}

avg_speed_game <- function(data) {
  data %>%
    group_by(player_name,play_id, game_id) %>%
    summarize(avg_speed = mean(s, na.rm = TRUE)) 
}

avg_speed_by_player(input_2023_w01)
avg_speed_game(input_2023_w01)
head(input_2023_w01)

```


```{r}
input_2023_w02 <- read.csv("C:/Users/marie/Downloads/nfl-big-data-bowl-2026-prediction/train/input_2023_w02.csv")
supplementary_data <- read.csv()

avg_speed_by_player(input_2023_w02)
```
```{r}
input_2023_w03 <- read.csv("C:/Users/marie/Downloads/nfl-big-data-bowl-2026-prediction/train/input_2023_w03.csv")

avg_speed_by_player(input_2023_w03)
```
```{r}
input_2023_w04 <- read.csv("C:/Users/marie/Downloads/nfl-big-data-bowl-2026-prediction/train/input_2023_w04.csv")

avg_speed_by_player(input_2023_w04)
```

```{r}
input_2023_w05 <- read.csv("C:/Users/marie/Downloads/nfl-big-data-bowl-2026-prediction/train/input_2023_w05.csv")

avg_speed_by_player(input_2023_w05)
```

```{r}
input_2023_w18 <- read.csv("C:/Users/marie/Downloads/nfl-big-data-bowl-2026-prediction/train/input_2023_w18.csv")

avg_speed_by_player(input_2023_w18)
```





#group each weeks games, find number of unique plays, how distinguish team 1 and 2? 
```{r}
unique_game <- function(data) {
  data %>%
    distinct(game_id, play_id) %>% 
    count(game_id, name = "num_unique_plays")
}

unique_game(input_2023_w01)
```

```{r}
first_instance <- input_2023_w01 %>%
  arrange(game_id, play_id, frame_id) %>%   # ensure earliest
  distinct(player_name, .keep_all = TRUE)

first_instance

first_play <- first_instance %>%
  filter(play_id == min(play_id))
first_play
s
```

Randomforest, a fail 
```{r}
```{r, include =FALSE, eval=FALSE}

#random tree hates missing values + character type so...
first_last_clean <- first_last %>% drop_na(x_last, y_last) 
first_last_clean <- first_last_clean %>% mutate(pos = as.factor(pos))

#this makes my R session just bug out and kick me out rip, I'm very sure I'm doing something wrong. But i wanna use ittttt
model2 <- rfsrc(Multivar(x_last, y_last) ~ x_1 + y_1 + s_1 + a_1 + dir_1 + pos, 
               data = first_last_clean)
```
```

